\documentclass[journal, letterpaper, draftclsnofoot, onecolumn, 10pt]{IEEEtran}

\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}

\usepackage{alltt}
\usepackage{float}
\usepackage{color}
\usepackage{url}
\usepackage{listings}

\usepackage{balance}
\usepackage[TABBOTCAP, tight]{subfigure}
\usepackage{enumitem}
\usepackage{pstricks, pst-node}
\usepackage{placeins}
\usepackage{geometry}
\usepackage{hyperref}
\geometry{textheight=8.5in, textwidth=6in}

\lstset{
  language=C,                % choose the language of the code
  numbers=left,                   % where to put the line-numbers
  stepnumber=1,                   % the step between two line-numbers.
  numbersep=5pt,                  % how far the line-numbers are from the code
  backgroundcolor=\color{white},  % choose the background color. You must add \usepackage{color}
  showspaces=false,               % show spaces adding particular underscores
  showstringspaces=false,         % underline spaces within strings
  showtabs=false,                 % show tabs within strings adding particular underscores
  tabsize=8,                      % sets default tabsize to 2 spaces
  captionpos=b,                   % sets the caption-position to bottom
  breaklines=true,                % sets automatic line breaking
  breakatwhitespace=true,         % sets if automatic breaks should only happen at whitespace
  title=\lstname,                 % show the filename of files included with \lstinputlisting;
}

%random comment

\newcommand{\cred}[1]{{\color{red}#1}}
\newcommand{\cblue}[1]{{\color{blue}#1}}

\newcommand{\toc}{\tableofcontents}


\def\name{Leon Leighton, Alec Merdler, Arthur Shing}

%% The following metadata will show up in the PDF properties
\hypersetup{
   colorlinks = true,
   urlcolor = black,
   linkcolor = black,
   pdfauthor = {\name},
   pdfkeywords = {cs444 ``operating systems'' files filesystem I/O},
   pdftitle = {CS 444 Project 1: Getting Acquainted},
   pdfsubject = {CS 444 Project 1},
   pdfpagemode = UseNone
}

\parindent = 0.0 in
\parskip = 0.1 in


\begin{document}
\title{Project 1: Getting Acquainted}
\author{Leon Leighton, Alec Merdler, and Arthur Shing}

\begin{titlepage}
    \pagenumbering{gobble}
    \centering
    \maketitle
    \begin{abstract}
      This document provides an overview of the work done by Group 11-09 for Project 1: Getting Acquainted.
      It includes the list of commands used to build our own kernel and verify that we booted it using QEMU on os-class.
      It also contains a description of the QEMU flags used to boot our kernel.
      Also included is the write up for our work on the Concurrency 1 programming assignment.
      This includes answers to questions asked in the assignment description, a work log, and the git version control log.
    \end{abstract}


\end{titlepage}
\pagenumbering{arabic}
\tableofcontents
\clearpage


\section{Project 1}
\subsection{Log of Commands}
After logging into os-class.
\begin{enumerate}
\item cd /scratch/spring2017/
\item mkdir 11-09
\item cd 11-09
\item git clone git://git.yoctoproject.org/linux-yocto-3.14
\item cd linux-yocto-3.14/
\item git checkout -b v3.14.26 v3.14.26
\item cd ..
\item source /scratch/opt/environment-setup-i586-poky-linux
\item qemu-system-i386 -gdb tcp::6609 -S -nographic -kernel bzImage-qemux86.bin -drive file=core-image-lsb-sdk-qemux86.ext3,if=virtio -enable-kvm -net none -usb -localtime --no-reboot --append "root=/dev/vda rw console=ttyS0 debug"
\item (In different terminal) gdb
\item (In different terminal) (gdb) target remote :6609
\item (In different terminal) (gdb) c
\item (In VM) uname -r
\item (In VM - output) 3.14.26ltsi-yocto-standard
\item cp /scratch/spring2017/files/config-3.14.26-yocto-qemu .config
\item cd linux-yocto-3.14/
\item (In menuconfig) Press / and type in LOCALVERSION, press enter
\item (In menuconfig) Hit 1, press enter and then edit the value to be -11-09-hw1
\item make menuconfig
\item make -j4 all
\item make bzImage
\item cd ..
\item qemu-system-i386 -gdb tcp::6609 -S -nographic -kernel linux-yocto-3.14/arch/x86/boot/bzImage -drive file=core-image-lsb-sdk-qemux86.ext3,if=virtio -enable-kvm -net none -usb -localtime --no-reboot --append "root=/dev/vda rw console=ttyS0 debug"
\item (In different terminal) gdb
\item (In different terminal) (gdb) target remote :6609
\item (In different terminal) (gdb) c
\item (In VM) uname -r
\item (In VM - output) 3.14.26-11-09-hw1
\end{enumerate}
\subsection{QEMU Flags}
\begin{itemize}
  \item -gdb: Wait for gdb connection on a device. In our case a tcp connection on port 6609.
  \item -S: Do not start CPU at startup. Forces typing 'c' in gdb
  \item -nographic: Disables graphical output
  \item -kernel: Kernel image to use
  \item -drive file,if: Which disk image file to use as a drive connected to an interface. In our case this is a connected to the virtio interface.
  \item -enable-kvm: Enable KVM virtualization support.
  \item -net: Network interface. In our case, none means to not setup a network interface.
  \item -usb: Enable USB driver
  \item -localtime: Set the real time clock to local time
  \item --no-reboot: Quite instead of rebooting.
  \item --append: Kernel command line option.
\end{itemize}
\clearpage
\section{Concurrency 1}
In this assignment, we attempted to implement a solution to the producer-consumer problem. The problem states that producers cannot
add to a shared buffer if the buffer is full, and consumers cannot take from the buffer if it is empty. Producer or consumer threads
must also have exclusive access to the buffer.

\subsection{Answers}
We think the main point of this assignment was to become familiar with multi-threaded programming. In this exercise, we
created multiple threads and managed how they interact with a shared resource. Managing how producers/consumers interact
with the buffer helped us practice using mutexes. Overall this assignment reminds us that managing shared resources is an
important part of concurrency programming.

We decided to utilize a mutex for the exercise to manage exclusive access to the buffer. A thread first locks the buffer, changes it,
and then unlocks it. While the mutex is locked, other threads are blocked until it is unlocked. Threads are also blocked from the buffer
while the buffer is full (for producers) or empty (for consumers). To implement the random number generator, we used a separate file that
generated numbers using rdrand or the Mersenne Twister, depending on support.

To test our implementation, we ran it with a smaller buffer to check if the blocks were occurring when the buffer was full or empty.
We also tested random number generation and thread handling by running it with a large amount of threads.

Overall, we learned how to use pthreads in c, and how we should consider synchronization problems when it comes to multithreaded programming.
We also learned how to correctly use version control systems, and the synchronization problems involved with those.

\subsection{Work Log}
All three members contributed to this homework assignment.
Members worked both remotely and met to work on the assignment in person.
Collaboration, when not in person, was primarily done through email and GitHub.
The majority of the programming was done Wednesday through Friday with most of the actual commits taking place on Friday.
\clearpage
\subsection{Version Control Log}
The Git Log is slightly inaccurate due to both in person collaboration and a delay in granting of rights to the repository.
\FloatBarrier
\begin{table}[h!]
\centering
\caption{Git Log}
% \label{git-log}
\begin{tabular}{|c|c|c|c|c|c|c|}
    \hline \textbf{Version} & \textbf{Author} & \textbf{Date} & \textbf{commit message} & \textbf{MF} & \textbf{AL} & \textbf{DL}  \\
    \hline 1 & alecmerdler & 2017-04-11 & initial commit & 2 & 0 & 0 \\
    \hline 2 & alecmerdler & 2017-04-13 & added .gitignore & 1 & 1 & 0 \\
    \hline 3 & alecmerdler & 2017-04-14 & starting concurrency \#1 & 2 & 49 & 1 \\
    \hline 4 & Lee Leighton & 2017-04-18 & Add our\_rand code. Uses rdrand or mt19937 to return random number & 5 & 309 & 0 \\
    \hline 5 & Lee Leighton & 2017-04-20 & Docs folder with latex files. Initial write for the qemu portion. & 3 & 262 & 0 \\
    \hline 6 & Lee Leighton & 2017-04-20 & Merge pull request \#1 from leel8on/leel8on/random & 0 & 0 & 0 \\
    \hline 7 & Lee Leighton & 2017-04-21 & Changing where buffer is created. Add mutex locking and creation of item & 2 & 46 & 6 \\
    \hline 8 & Lee Leighton & 2017-04-21 & Fix how consumer access the item & 1 & 3 & 4 \\
    \hline 9 & Lee Leighton & 2017-04-21 & Add multiple threads for both consumer and producer specified as arguments & 1 & 28 & 16 \\
    \hline 10 & Lee Leighton & 2017-04-21 & Fix for loop index intialization & 1 & 3 & 3 \\
    \hline 11 & Lee Leighton & 2017-04-21 & Use same number of threads for both consumers and producers & 1 & 6 & 7 \\
    \hline 12 & Lee Leighton & 2017-04-21 & Keep track of threads ids in one array & 1 & 9 & 8 \\
    \hline 13 & Arthur Shing & 2017-04-21 & Moved seed generation to hw1.c & 2 & 6 & 3 \\
    \hline
\end{tabular}
\begin{tabular}{lp{12cm}}
  \label{tabular:legend:git-log}
  \textbf{acronym} & \textbf{meaning} \\
  V & \texttt{version} \\
  MF & Number of \texttt{modified files}. \\
  AL & Number of \texttt{added lines}. \\
  DL & Number of \texttt{deleted lines}. \\
\end{tabular}
\end{table}
\FloatBarrier
\end{document}
