\documentclass[journal, letterpaper, draftclsnofoot, onecolumn, 10pt]{IEEEtran}

\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}

\usepackage{alltt}
\usepackage{float}
\usepackage{color}
\usepackage{url}
\usepackage{listings}

\usepackage{balance}
\usepackage[TABBOTCAP, tight]{subfigure}
\usepackage{enumitem}
\usepackage{pstricks, pst-node}
\usepackage{placeins}
\usepackage{geometry}
\usepackage{hyperref}
\geometry{textheight=8.5in, textwidth=6in}

\lstset{
  language=C,                % choose the language of the code
  numbers=left,                   % where to put the line-numbers
  stepnumber=1,                   % the step between two line-numbers.
  numbersep=5pt,                  % how far the line-numbers are from the code
  backgroundcolor=\color{white},  % choose the background color. You must add \usepackage{color}
  showspaces=false,               % show spaces adding particular underscores
  showstringspaces=false,         % underline spaces within strings
  showtabs=false,                 % show tabs within strings adding particular underscores
  tabsize=8,                      % sets default tabsize to 2 spaces
  captionpos=b,                   % sets the caption-position to bottom
  breaklines=true,                % sets automatic line breaking
  breakatwhitespace=true,         % sets if automatic breaks should only happen at whitespace
  title=\lstname,                 % show the filename of files included with \lstinputlisting;
}

%random comment

\newcommand{\cred}[1]{{\color{red}#1}}
\newcommand{\cblue}[1]{{\color{blue}#1}}

\newcommand{\toc}{\tableofcontents}


\def\name{Leon Leighton, Alec Merdler, Arthur Shing}

%% The following metadata will show up in the PDF properties
\hypersetup{
   colorlinks = true,
   urlcolor = black,
   linkcolor = black,
   pdfauthor = {\name},
   pdfkeywords = {cs444 ``operating systems'' files encryption block driver},
   pdftitle = {CS 444 Project 3: The Kernel Crypto API},
   pdfsubject = {CS 444 Project 3},
   pdfpagemode = UseNone
}

\parindent = 0.0 in
\parskip = 0.1 in


\begin{document}
\title{Project 3: The Kernel Crypto API}
\author{Leon Leighton, Alec Merdler, and Arthur Shing}

\begin{titlepage}
    \pagenumbering{gobble}
    \centering
    \maketitle
    \begin{abstract}
      This document provides an overview of the work done by Group 11-09 for Project 3: The Kernel Crypto API.
      It includes the design we used to implement the encryption algorithm.
      This includes answers to questions asked in the assignment description, a work log, and the git version control log.
    \end{abstract}


\end{titlepage}
\pagenumbering{arabic}
\tableofcontents
\clearpage

\section{Project 3}

\subsection{Design}
To begin, we based the structure of our design off of a simple block driver written by Jonathan Corbet and modified by Pat Patterson at \url{http://blog.superpat.com/2010/05/04/a-simple-block-driver-for-linux-kernel-2-6-31}, which was written for the 2.6.0 version of the kernel.

In our design, we use a 32 bit key for the encryption. Because this is a block cypher, we knew that we could have more data being read/written
than the amount of data that fits in one block. To accomodate for this, we encrypt/decrypt data in increments of block size.
We implemented the data encryption/decryption in the transfer function, where data is transferred to and from the device. \\


\subsection{Answers}

% What do you think the main point of this assignment is?

We think that the main point of this assignment was to learn how to work with the Linux Kernel's Crypto API, and to practice working with memory allocation.
In this assignment, we created a RAM Disk device driver for the Linux Kernel and encrypted/decrypted data that is written and read by the device. \\
% How did you personally approach the problem? Design decisions, algorithm, etc.

To approach the problem, it was important to first understand how block drivers work.
By gleaning LDD3, we were able to understand the basic methods that the kernel calls to get the driver to process reads and writes on the device.
After we wrote a sufficient block driver, we compiled it as a module (sbd.ko) and loaded it into the kernel with insmod sbd.ko.
For encryption, we used AES as our algorithm and called the provided Crypto API using crypto\_alloc\_cipher(). \\

% TESTING DETAILS

To test our implementation, we compiled the block driver as a module and loaded it into the kernel.
After loading it as a module, we write zeroes into the device. Then, we created a filesystem and mounted the device.
We echoed some text into the device and then searched for the text, which did not print anything.
This showed us that the text was encrypted.

\begin{itemize}
    \item insmod sbd.ko
    \item shred -z /dev/sbd0
    \item mkfs.ext2 /dev/sbd0
    \item mount /dev/sbd0 /mnt
    \item echo 'hello' > /mnt/hello
    \item grep -a 'hello' /dev/sbd0
\end{itemize}


% What did you learn?

Overall, we learned how to implement block device drivers in the Linux Kernel and also how to work with the Kernel's Crypto API.
We also learned about the operations and methods that block devices have and use. \\


\subsection{Work Log}
We began work on the concurrency exercise in recitation. We worked on the concurrency exercise over the next few days.
We used existing code to create a template for the block driver on and had a usable driver on 5/21.
We set up the encryption/decryption on 5/22 and tested it the same day.



\clearpage
\subsection{Version Control Log}



\FloatBarrier



\scalebox{0.8}{
\input{vclog.tex}}


\FloatBarrier
\end{document}
